Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-04 article.tex
wording

 % change the arguments, as appropriate, in the following:
\jmlrvolume{1}
\jmlryear{2010}
\jmlrworkshop{Neural Connectomics Workshop}

@@

% Correlation => Issue indirect effect
% Partial correlation => better estimate of the graph  => Symmetric measure
While the correlation coefficient is unable to distinguish between
direct and indirect interaction, the partial correlation coefficient
aims to infer only direct ones through the conditioning over all the other
variables. In previous study \cite{shipley2002cause}, it has been suggested
consider correlation coefficients of all possible orders,
i.e. conditioned on every subsets of the set of $p-2$ other variables, in order
to take into account multiple indirect paths between a given pair of variables.
An obvious limitation to calculate high-order coefficient is the number of
samples in conditioned data sets \textcolor{red}{AJ: Est ce que ce ne sera pas
à la fois $p$ and $n$?}. Given the high number of samples $n$
in the Connectomics challenge, we only consider the highest order of partial
correlation coefficient.

Since the partial correlation is symmetric, it is not possible to infer the causal
mechanism behind the interaction (I directly causes J, J directly causes I or
both ). Furthermore two other causal mechanisms may be implied
by a non-zero partial coefficient. First, the pair of variables may be induced
by a common (hidden) variable and second, I (respectively J) is conditionally
correlated to a hidden variable affecting J (resp. I) \cite{de2004discovery}.

>>>>

 % change the arguments, as appropriate, in the following:
\jmlrvolume{1}
\jmlryear{2014}
\jmlrworkshop{Neural Connectomics Workshop}

@@

% Correlation => Issue indirect effect
% Partial correlation => better estimate of the graph  => Symmetric measure
While the correlation coefficient is unable to distinguish between
direct and indirect interaction, the partial correlation coefficient
aims to infer only direct ones through the conditioning over all the other
variables. In previous study \cite{shipley2002cause}, it has been suggested to
consider correlation coefficients of all possible orders,
i.e. conditioned on every subsets of the set of $p-2$ other variables. This
would take into account multiple indirect paths between a given pair of
variables. An obvious limitation to estimate correctly high-order coefficients
is the number of samples. However given the high number of samples $n$
in the Connectomics challenge, we only consider the highest order of partial
correlation coefficient.

Since the partial correlation is a symmetric, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
be infered. Moreover, two other causal mechanisms might be implied while having
a non-zero partial coefficient: (i) a pair of variables is induced by a
common (hidden) variable; (ii) $A$ (respectively $B$) is conditionally
correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.
